Covariates analysis of MSBB RNASeq data of region BM 36 (realigned from source FASTQ with STAR-HTSeq)

### 2016-09-20 code/Rmd/MSSM_BM_36_RNASeq.Rmd
Added markdown to process BM36 from MSSM aligned and processed by Eli-Lilly

# Store differential expression results
write.table(DE, file = 'diffExpression.tsv', sep = '\t', row.names=F, quote=F)
dexp_obj = File('diffExpression.tsv', name = 'Differential Expression Analysis', parentId = CODE$properties$id)
dexp_obj = synStore(dexp_obj, used = ALL_USED_IDs, activityName = activityName, 
                    executed = thisFile, activityDescription = activityDescription)
```
|  *Results*            |  *SynapseID*                    |
  |  -------              |   ---------                     |
  |  Covariates           |  `r covar_obj$properties$id`    |
  |  Residual Expression  |  `r expr_obj$properties$id`     |
  |  Differential Expression  |  `r dexp_obj$properties$id` |

>>>>

# Store differential expression results
write.table(DE, file = 'diffExpression.tsv', sep = '\t', row.names=F, quote=F)
dexp_obj = File('diffExpression.tsv', name = 'Differential Expression Analysis', parentId = CODE$properties$id)
dexp_obj = synStore(dexp_obj, used = ALL_USED_IDs, activityName = activityName, 
                    executed = thisFile, activityDescription = activityDescription)

# Store logcpm values
write.table(VOOM.ADJUSTED.GENE_EXPRESSION$E, file = 'logCPM.tsv', sep = '\t', row.names=T, quote=F)
exp1_obj = File('logCPM.tsv', name = 'Raw logCPM', parentId = CODE$properties$id)
exp1_obj = synStore(exp1_obj, used = ALL_USED_IDs, activityName = activityName, 
                   executed = thisFile, activityDescription = activityDescription)
```
|  *Results*            |  *SynapseID*                    |
  |  -------              |   ---------                     |
  |  Covariates           |  `r covar_obj$properties$id`    |
  |  Residual Expression  |  `r expr_obj$properties$id`     |
  |  Differential Expression  |  `r dexp_obj$properties$id` |

### 2016-09-20 code/Rmd/MSSM_BM_36_RNASeq_Realigned_StarHTSeq2.Rmd
Added markdown to process BM36 from MSSM aligned and processed by Eli-Lilly

# Store logcpm values
write.table(VOOM.ADJUSTED.GENE_EXPRESSION$E, file = 'logCPM.tsv', sep = '\t', row.names=F, quote=F)
exp1_obj = File('logCPM.tsv', name = 'Raw logCPM', parentId = CODE$properties$id)
exp1_obj = synStore(exp1_obj, used = ALL_USED_IDs, activityName = activityName, 
                   executed = thisFile, activityDescription = activityDescription)

>>>>

# Store logcpm values
write.table(VOOM.ADJUSTED.GENE_EXPRESSION$E, file = 'logCPM.tsv', sep = '\t', row.names=T, quote=F)
exp1_obj = File('logCPM.tsv', name = 'Raw logCPM', parentId = CODE$properties$id)
exp1_obj = synStore(exp1_obj, used = ALL_USED_IDs, activityName = activityName, 
                   executed = thisFile, activityDescription = activityDescription)

### 2016-09-20 code/Rmd/MSSM_BM_36_RNASeq_Reprocessed_LillyPipeline.Rmd
Added markdown to process BM36 from MSSM aligned and processed by Eli-Lilly

knit2synapse::knitToFolderEntity(file = "./MSSM_BM_44_RNASeq_Reprocessed_LillyPipeline.Rmd",
                                 parentId ="syn5570248",
                                 entityName = 'MSBB BM 44 RNASeq Reprocessed LillyPipeline')
```

@@

```{r synapse.parameters, include=FALSE, cache=TRUE}
# Synapse parameters
parentId = 'syn5570248';
activityName = 'Covariate analysis';
activityDescription = 'Covariate analysis of MSBB BM 44 RNASeq samples';

thisFileName <- 'MSSM_BM_44_RNASeq_Reprocessed_LillyPipeline.Rmd'

# Github link
thisRepo <- getRepo(repository = "th1vairam/Brain_Reg_Net", ref="branch", refName='AMPAD')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('code/Rmd/',thisFileName))
```
Data were obtained from AMP-AD portal of MSSM, and following brain regions were analysed for differential expression between case and control:
  | Region | Name                        | 
  | :----- | --------------------------- | 
  | BM_44  | inferior frontal Gyrus (IFG)|

* BM 44: pars opercularis (of the inferior frontal gyrus), and it refers to a subdivision of the frontal region of cerebral cortex.

@@

METADATA = left_join(METADATA_TECHNICAL %>%
                       dplyr::mutate(ID = gsub('hB_RNA_','',NewBarcode),
                                     ID = as.numeric(ID)),
                     METADATA_CLINICAL %>%
                       dplyr::select(BB, BM.44.Barcode, BM36.Fnl, BM22.Fnl, BM10.Fnl, PMI, RACE, 
                                     AOD, CDR, SEX, NP.1, PlaqueMean, bbscore) %>%
                       dplyr::rename(BM_44 = BM.44.Barcode,
                                     BM_10 = BM10.Fnl,
                                     BM_22 = BM22.Fnl,
                                     BM_36 = BM36.Fnl) %>%
                       tidyr::gather(BrainRegion, ID, -BB, -PMI, -RACE, 
                                     -AOD, -CDR, -SEX, -NP.1, -PlaqueMean, -bbscore) %>%
                       filter(!is.na(ID)) %>%
                       dplyr::mutate(ID = as.numeric(ID))) %>%
  inner_join(SampleID) %>%
  filter(!is.na(SampleID)) %>%
  unique %>%
  filter(BrainRegion == 'BM_44', !(SampleID %in% c('hB_RNA_8565', 'hB_RNA_4919', 'hB_RNA_9005')))
rownames(METADATA) = METADATA$SampleID

@@

### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
# Code
CODE <- Folder(name = 'MSBB BM 44 RNASeq Reprocessed LillyPipeline', parentId = parentId)
CODE <- synStore(CODE)

>>>>

knit2synapse::knitToFolderEntity(file = "./MSSM_BM_36_RNASeq_Reprocessed_LillyPipeline.Rmd",
                                 parentId ="syn5570248",
                                 entityName = 'MSBB BM 36 RNASeq Reprocessed LillyPipeline')
```

@@

```{r synapse.parameters, include=FALSE, cache=TRUE}
# Synapse parameters
parentId = 'syn5570248';
activityName = 'Covariate analysis';
activityDescription = 'Covariate analysis of MSBB BM 36 RNASeq samples';

thisFileName <- 'MSSM_BM_36_RNASeq_Reprocessed_LillyPipeline.Rmd'

# Github link
thisRepo <- getRepo(repository = "th1vairam/Brain_Reg_Net", ref="branch", refName='AMPAD')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('code/Rmd/',thisFileName))
```

@@

METADATA = left_join(METADATA_TECHNICAL %>%
                       dplyr::mutate(ID = gsub('hB_RNA_','',NewBarcode),
                                     ID = as.numeric(ID)),
                     METADATA_CLINICAL %>%
                       dplyr::select(BB, BM.44.Barcode, BM36.Fnl, BM22.Fnl, BM10.Fnl, PMI, RACE, 
                                     AOD, CDR, SEX, NP.1, PlaqueMean, bbscore) %>%
                       dplyr::rename(BM_44 = BM.44.Barcode,
                                     BM_10 = BM10.Fnl,
                                     BM_22 = BM22.Fnl,
                                     BM_36 = BM36.Fnl) %>%
                       tidyr::gather(BrainRegion, ID, -BB, -PMI, -RACE, 
                                     -AOD, -CDR, -SEX, -NP.1, -PlaqueMean, -bbscore) %>%
                       filter(!is.na(ID)) %>%
                       dplyr::mutate(ID = as.numeric(ID))) %>%
  inner_join(SampleID) %>%
  filter(!is.na(SampleID)) %>%
  unique %>%
  filter(BrainRegion == 'BM_36', !(SampleID %in% c('hB_RNA_8565', 'hB_RNA_4919', 'hB_RNA_9005')))
rownames(METADATA) = METADATA$SampleID

@@

### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
# Code
CODE <- Folder(name = 'MSBB BM 36 RNASeq Reprocessed LillyPipeline', parentId = parentId)
CODE <- synStore(CODE)
